### 2016-03-05 doc/paper/project.tex
papering

done:

feature:

+ auto sym
+ off the shelf
+ better branch coverage than pure event sequences

related:

+ catg, we use it to java gui
+ guitar, we cover branch

problem:

+ number? write a small program for catg
+ how jfp-awt do choice generator?
+ barad event sequences

aut
+ ticket
+ workout generator
+ jnotepad
+ capivara
+ jeditor

paper
+ modified files
        modified:   instrument/SnoopInstructionMethodAdapter.java  -- fix catg bug
        modified:   instrument/SnoopInstructionTransformer.java  -- modify which pachage should be instrumented
        modified:   interpreters/StaticInvocation.java  -- add parseInt support, add symbolic int to symbolic stack
        modified:   interpreters/StringValue.java    -- add two flags, one for IntValue.symbol, the other for binding accessibleName
        modified:   solvers/CVC4Solver.java  -- write back int concrete value to string input

src/main/java/guicat/
├── config
│   ├── GCConfig.java
│   └── GCEntry.java
├── SymAgent.java    -- agent to instrument gui
├── SymbolicEntry.java  -- symboli tables, singletons
├── SymbolicMirror.java
└── SymbolicTable.java

feature
+ instrument gui
+ symbolic table
+ parseInt
+ user conf, format

### 2016-03-28 src/main/java/examples/workout/Main.java
workout src

@@ -1,0 +1,460 @@
+package examples.workout;
+
+
+import javax.swing.*;
+import java.awt.*;
+import java.awt.event.ActionEvent;
+import java.awt.event.ActionListener;
+
+public class Main extends JFrame {
+    JLabel genderLabel;
+    JLabel metabolismLabel;
+    JLabel experienceLabel;
+    JLabel ageLabel;
+    JLabel heightLabel;
+    JLabel weightLabel;
+    JComboBox<String> genderCombo;
+    JComboBox<String> metabolismCombo;
+    JComboBox<String> experienceCombo;
+    JTextField ageTextField;
+    JTextField heightTextField;
+    JTextField weightTextField;
+    JButton generateButton;
+    JButton clearButton;
+    JTextArea resultTextArea;
+
+    public Main() {
+        JPanel contentPane = new JPanel(new GridBagLayout());
+        this.setContentPane(contentPane);
+        setDefaultCloseOperation(JFrame.EXIT_ON_CLOSE);
+
+        GridBagConstraints gbc = new GridBagConstraints(0, 0, 1, 1, 0, 0, GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0);
+
+        {
+            genderLabel = new JLabel("Gender");
+            genderCombo = new JComboBox<>(new String[] {"Male", "Female"});
+            contentPane.add(genderLabel,gbc);
+            gbc.gridx = 0;
+            gbc.gridy = 1;
+            contentPane.add(genderCombo, gbc);
+            genderLabel.setLabelFor(genderCombo);
+        }
+
+        {
+            metabolismLabel = new JLabel("Metabolism");
+            metabolismCombo = new JComboBox<>(new String[] {"Slow", "Normal", "Fast"});
+            gbc.gridx = 1;
+            gbc.gridy = 0;
+            contentPane.add(metabolismLabel, gbc);
+            gbc.gridx = 1;
+            gbc.gridy = 1;
+            contentPane.add(metabolismCombo, gbc);
+            metabolismLabel.setLabelFor(metabolismCombo);
+        }
+
+        {
+            experienceLabel = new JLabel("Experience");
+            experienceCombo = new JComboBox<>(new String[] {"Beginner", "Intermediate", "Advanced"});
+            gbc.gridx = 2;
+            gbc.gridy = 0;
+            contentPane.add(experienceLabel, gbc);
+            gbc.gridx = 2;
[…]

### 2016-03-28 src/main/java/guicat/testcase/Generator.java
small

@@ -56,7 +56,7 @@ public class Generator {
                      Node eNode = elements.item(j);
                      if (eNode.getNodeType() == Node.ELEMENT_NODE) {
                          Element element = (Element) eNode;
-                         System.out.println("\n----" + element.getNodeName() + " : " + element.getTextContent().trim());
+                      //   System.out.println("\n----" + element.getNodeName() + " : " + element.getTextContent().trim());
                          if (element.getNodeName().trim().equals("Name") ) {
                              key = element.getTextContent();
                          }
@@ -77,7 +77,7 @@ public class Generator {
                      key = "";
                      title = "";
                      ID = "";
-             }
+                }
              }
          }
       } catch (Exception e) {
@@ -95,8 +95,8 @@ public class Generator {
         String branchDir = "./log/ticket/branches";
         String guicatTestcaseDir = "./log/ticket/gctestcases";
 
-   //    String guiFile = "./log/ticket/ticket.GUI";
-        String guiFile = "./log/argouml/argouml.GUI";
+       String guiFile = "./log/ticket/ticket.GUI";
+    //    String guiFile = "./log/argouml/argouml.GUI";
         Map map = Generator.getNameIDMap(guiFile);
         System.out.println(map.toString());
 

### 2016-03-28 guicat.sh
guicat generate testcase

@@ -1,6 +1,11 @@
 #!/usr/bin/env bash
+if [ -z $1 ]; then
+    echo "Usage: ./guicat ./conf/ticket/ticket.conf"
+    exit
+fi
 
-. ./conf/ticket/ticket.conf
+#. ./conf/ticket/ticket.conf
+. $1
 
 classpath="."
 for jar in `ls lib`

### 2016-03-28 jacoco.sh

@@ -1,3 +1,4 @@
+#!/usr/bin/env bash
 #check args
 if [ -z $1 ] || [ -z $2 ]; then
     echo "Usage: $0 autId guitar|guicat"

### 2016-03-28 src/main/java/examples/workout/Main.java

@@ -142,9 +142,16 @@ public class Main extends JFrame {
                 String gender = (String)genderCombo.getSelectedItem();
                 String metabolism = (String)metabolismCombo.getSelectedItem();
                 String experience = (String)experienceCombo.getSelectedItem();
-                int age = Integer.parseInt(ageTextField.getText().trim());
-                float height = Float.parseFloat(heightTextField.getText().trim());
-                float weight = Float.parseFloat(weightTextField.getText().trim());
+                int age = 1;
+                float height = 100;
+                float weight = 100;
+                try {
+                     age = Integer.parseInt(ageTextField.getText().trim());
+                     height = Float.parseFloat(heightTextField.getText().trim());
+                     weight = Float.parseFloat(weightTextField.getText().trim());
+                } catch (Exception ex) {
+                    ;
+                }
                 //Auiliary variables for coeficients
                 int repCoeficient = 0;
                 int setCoeficient = 0;

### 2016-03-28 src/main/java/guicat/config/GCConfig.java

@@ -35,7 +35,7 @@ public class GCConfig {
             while ((line = reader.readLine()) != null) {
                 line=line.trim();
                 if (line.isEmpty() || line.startsWith("#")) continue;
-                System.out.println(line);
+              //  System.out.println(line);
                 String delims = ",";
                 String[] tokens = line.split(delims);
                 assert tokens.length == 4 : "guicat file format error.";

### 2016-03-28 src/main/java/guicat/testcase/Generator.java

@@ -1,105 +1,272 @@
 package guicat.testcase;
 
-import org.w3c.dom.Document;
-import org.w3c.dom.Element;
-import org.w3c.dom.Node;
-import org.w3c.dom.NodeList;
+import guicat.config.GCConfig;
+import org.w3c.dom.*;
 
 import javax.xml.parsers.DocumentBuilder;
 import javax.xml.parsers.DocumentBuilderFactory;
-import java.io.File;
-import java.util.HashMap;
-import java.util.Map;
+import javax.xml.transform.Transformer;
+import javax.xml.transform.TransformerFactory;
+import javax.xml.transform.dom.DOMSource;
+import javax.xml.transform.stream.StreamResult;
+import java.io.*;
+import java.util.*;
 
 /**
  * Created by Lin Cheng on 27/03/16.
  */
 public class Generator {
-    String appConf = "";
-    String guicatConf = "";
+   // String appConf = "";
+   // String guicatConf = "";
+    String guiFile = "";
     String guitarTestcaseDir = "";
     String branchDir = "";
     String guicatTestcaseDir = "";
 
-    public Generator(String appConf, String guicatConf, String guitarTestcaseDir, String branchDir, String guicatTestcaseDir) {
-        this.appConf = appConf;
-        this.guicatConf = guicatConf;
+    private static Map<String, String> bind = null;
+    synchronized public static Map<String, String> getGUINameIDBindMap(String guiFile) {
+        if (bind == null)
+            bind = getNameIDMap(guiFile);
+        return bind;
+    }
+
+    public Generator( String guiFile, String guitarTestcaseDir, String branchDir, String guicatTestcaseDir) {
+       // this.appConf = appConf;
+      //  this.guicatConf = guicatConf;
+        this.guiFile = guiFile;
         this.guitarTestcaseDir = guitarTestcaseDir;
         this.branchDir = branchDir;
         this.guicatTestcaseDir = guicatTestcaseDir;
     }
 
-    public static Map<String, String> getNameIDMap(String guiFile) {
+    private static Map<String, String> getNameIDMap(String guiFile) {
         String title = "";
         String ID = "";
         String key = "";
         Map<String, String> ret = new HashMap<String, String>();
-      try {
-         File inputFile = new File(guiFile);
-         DocumentBuilderFactory dbFactory
-            = DocumentBuilderFactory.newInstance();
-         DocumentBuilder dBuilder = dbFactory.newDocumentBuilder();
-         Document doc = dBuilder.parse(inputFile);
[…]

### 2016-03-28 workout.sh

@@ -1,6 +1,6 @@
 #!/usr/bin/env bash
 
-. ./conf/ticket/ticket.conf
+. ./conf/workout/workout.conf
 
 classpath="."
 for jar in `ls lib`
@@ -40,16 +40,8 @@ eval $testcaseCmd
 for testcase in `find $AUTTESTCASE -type f -name "*.tst" -printf '%f\n'`
 do
     testcase_id=${testcase%????}
-    python concolic.py -Dguicat.conf=$guicatConfigFile -v 32 --autosym -t $testcase_id edu.umd.cs.guitar.replayer.JFCReplayerMain "-c $AUT_MAINCLASS -g $guiFile -e $efgFile -t $AUTDIR/testcases/$testcase_id.tst -i 2000 -d 200 -l $AUTDIR/logs/$testcase_id.log -gs $AUTDIR/states/$testcase_id.sta -cf $configurationFile -ts"
+    python concolic.py -Dguicat.conf=conf/ticket/guicat.properties -v 32 --autosym -t $testcase_id edu.umd.cs.guitar.replayer.JFCReplayerMain "-c $AUT_MAINCLASS -g $guiFile -e $efgFile -t $AUTDIR/testcases/$testcase_id.tst -i 2000 -d 200 -l $AUTDIR/logs/$testcase_id.log -gs $AUTDIR/states/$testcase_id.sta -cf $configurationFile -ts"
 #break
 done
 
 mv branches $AUTDIR
-
-#create guicat testcases
-cmd="java -Dguicat.conf=$guicatConfigFile -cp $classpath guicat.testcase.Generator $guiFile $AUTTESTCASE $branchDir $autGuicatTestcase"
-echo $cmd
-eval $cmd
-
-./jacoco.sh $AUT guitar
-./jacoco.sh $AUT guicat

### 2016-03-29 gctestcase.sh
add aut jnotepad, not so satisfied

@@ -1,0 +1,25 @@
+#create guicat testcases
+. ./conf/workout/workout.conf
+
+classpath="."
+for jar in `ls lib`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./lib/"$jar
+    fi
+done
+
+for jar in `ls aut`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./aut/"$jar
+    fi
+done
+cmd="java -Dguicat.conf=$guicatConfigFile -cp $classpath guicat.testcase.Generator $guiFile $AUTTESTCASE $branchDir $autGuicatTestcase"
+echo $cmd
+eval $cmd
+
+
+./jacoco.sh $AUT guicat

### 2016-03-29 src/main/java/examples/jnotepad/Actions.java

@@ -1,0 +1,469 @@
+package examples.jnotepad;
+
+//import the packages for using the classes in them into this class
+import java.io.*;
+import java.util.*;
+import java.awt.*;
+import java.awt.event.*;
+import javax.swing.*;
+import javax.swing.filechooser.*;
+
+/**
+ *A PUBLIC CLASS FOR ACTIONS.JAVA
+ */
+public class Actions{
+	//declaration of the private variables used in the program
+	private int returnVal; //for JFileChooser
+	private int option; //for using it into JOptionPane 
+	private String fileContent = null; //to get the text from the text area
+	private String fileName = null; //for using the name of the file
+	private String findword; //for searching & finding the word
+	private JFileChooser jfc = new JFileChooser("."); //for using a open & save dialog
+	private ExampleFileFilter filter = new ExampleFileFilter(); //for filtering the file
+	Notepad n; //for using the object in the Notepad.java
+	public Fonts font = new Fonts();
+
+	public Actions(Notepad n){
+		this.n = n;
+	}
+	/**
+	 *If we want to write a new text, first we want to know if the text area is empty or not,
+	 *second we want to kwnow if the text was saved or not.
+	 *If the text area isn't empty & the text wasn't saved befor this time, then the program display ->
+	 *for the user an option for saving the text in a new file or in the same file
+	 */
+	public void neW(){
+		/**
+		 *if the text area isn't empty & if the text area hasn't 
+		 *a text not saved befor (fileContent != null)
+		 */
+		if(!n.getTextArea().getText().equals("") && !n.getTextArea().getText().equals(fileContent)){
+			/**
+			 *here, we have 2 thing, first if the text wasn't be opened or saved befor
+			 *second if the text was be opened or saved
+			 */
+			//if there was no file opened or saved
+			if(fileName == null){
+				/**
+				 *this method has 3 options (1 = YES, 2 = NO, 3 = Cancel)
+				 *this is an option pop up to the user, for saving the old text or not
+				 */
+				option = JOptionPane.showConfirmDialog(null,"Do you want to save the changes ??");
+				//if the user click on YES button, 
+				//then the program will save the text & make a new text area
+				if(option == 0){
+					//to save the text into a new file
+					saveAs();
+					//to create new getTextArea() after saving the old getTextArea()
+					n.getTextArea().setText("");
+				}
+				//if the user click on NO button
+				if(option == 1){
[…]

### 2016-03-29 src/main/java/examples/jnotepad/Center.java

@@ -1,0 +1,26 @@
+package examples.jnotepad;
+//import the packages for using the classes in them into this class
+import java.awt.*;
+/**
+ *A PUBLIC CLASS FOR CENTER.JAVA
+ */
+public class Center{
+	Notepad n; //for using the object in the Notepad.java
+	Fonts f; //for using the object in the Fonts.java
+	public Center(Notepad n){
+		this.n = n;
+	}
+	public Center(Fonts f){
+		this.f = f;
+	}
+	public void nCenter(){
+		//Centering the window
+		Dimension screenSize = Toolkit.getDefaultToolkit().getScreenSize();
+		n.setLocation((screenSize.width-n.getWidth())/2,(screenSize.height-n.getHeight())/2);
+	}
+	public void fCenter(){
+		//Centering the window
+		Dimension screenSize = Toolkit.getDefaultToolkit().getScreenSize();
+		f.setLocation((screenSize.width-f.getWidth())/2,(screenSize.height-f.getHeight())/2);
+	}
+}

### 2016-03-29 src/main/java/examples/jnotepad/ExampleFileFilter.java

@@ -1,0 +1,275 @@
+package examples.jnotepad;
+
+/*
+ * Copyright (c) 2002 Sun Microsystems, Inc. All  Rights Reserved.
+ * 
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions
+ * are met:
+ * 
+ * -Redistributions of source code must retain the above copyright
+ *  notice, this list of conditions and the following disclaimer.
+ * 
+ * -Redistribution in binary form must reproduct the above copyright
+ *  notice, this list of conditions and the following disclaimer in
+ *  the documentation and/or other materials provided with the distribution.
+ * 
+ * Neither the name of Sun Microsystems, Inc. or the names of contributors
+ * may be used to endorse or promote products derived from this software
+ * without specific prior written permission.
+ * 
+ * This software is provided "AS IS," without a warranty of any kind. ALL
+ * EXPRESS OR IMPLIED CONDITIONS, REPRESENTATIONS AND WARRANTIES, INCLUDING
+ * ANY IMPLIED WARRANTY OF MERCHANTABILITY, FITNESS FOR A PARTICULAR PURPOSE
+ * OR NON-INFRINGEMENT, ARE HEREBY EXCLUDED. SUN AND ITS LICENSORS SHALL NOT
+ * BE LIABLE FOR ANY DAMAGES OR LIABILITIES SUFFERED BY LICENSEE AS A RESULT
+ * OF OR RELATING TO USE, MODIFICATION OR DISTRIBUTION OF THE SOFTWARE OR ITS
+ * DERIVATIVES. IN NO EVENT WILL SUN OR ITS LICENSORS BE LIABLE FOR ANY LOST
+ * REVENUE, PROFIT OR DATA, OR FOR DIRECT, INDIRECT, SPECIAL, CONSEQUENTIAL,
+ * INCIDENTAL OR PUNITIVE DAMAGES, HOWEVER CAUSED AND REGARDLESS OF THE THEORY
+ * OF LIABILITY, ARISING OUT OF THE USE OF OR INABILITY TO USE SOFTWARE, EVEN
+ * IF SUN HAS BEEN ADVISED OF THE POSSIBILITY OF SUCH DAMAGES.
+ * 
+ * You acknowledge that Software is not designed, licensed or intended for
+ * use in the design, construction, operation or maintenance of any nuclear
+ * facility.
+ */
+
+/*
+ * @(#)ExampleFileFilter.java	1.13 02/06/13
+ */
+
[…]

### 2016-03-29 src/main/java/examples/jnotepad/Fonts.java

@@ -1,0 +1,98 @@
+package examples.jnotepad;
+
+
+//import the packages for using the classes in them into this class
+import java.awt.*;
+import java.awt.event.*;
+import javax.swing.*;
+
+/**
+ *A class for creating JFontDialog
+ */
+public class Fonts extends JDialog{
+	/**
+	 *@see Center.java
+	 *this class to make the JDialog in the center
+	 */
+	public Center center = new Center(this);
+	
+	//declaration of the private variables used in the program
+	private JPanel jp = new JPanel();
+	private JLabel fjl = new JLabel("Fonts: ");
+	private JComboBox fjcb = new JComboBox();
+	/**
+	 *-> GraphicsEnvironment.getLocalGraphicsEnvironment().getAvailableFontFamilyNames() <-
+	 *		WE USING THIS METHOD TO GET ALL FONT IN THE SYSTEM (OS)
+	 */
+	private String fonts[]=GraphicsEnvironment.getLocalGraphicsEnvironment().getAvailableFontFamilyNames();
+	private JLabel sjl = new JLabel("Sizes: ");
+	private JComboBox sjcb = new JComboBox();
+	private String sizes[] = {"8","10","12","14","16","18","20","24","28","32","48","72"};
+	private JLabel tjl = new JLabel("Types: ");
+	private JComboBox tjcb = new JComboBox();
+	private String types[] = {"Regular", "Bold", "Italic", "Bold Italic"};
+	private JLabel jjl = new JLabel("Preview:");
+	private JLabel jl = new JLabel("AaBaCcDdeEfFgGhHjJ");
+	private JButton okjb = new JButton("OK");
+	private JButton cajb = new JButton("Cancel");
+	//for using ok & cancel button @Actions.java
+	public JButton getOkjb(){
+		return okjb;
+	}
+	public JButton getCajb(){
+		return cajb;
+	}
+	//Constructor of Fonts
+	public Fonts(){
+		//for setting the title
+		setTitle("Font Dialog");
+		setResizable(false);
+		/**
+		 *setting the layout (GridLayout: 5 rows & 2 columns)
+		 *add font JLabel, add font JComboBox
+		 *add type JLabel, add type JComboBox
+		 *add size JLabel, add size JComboBox
+		 *add preview JLabel,add test JLabel
+		 *add ok button, add cancel button
+		 */
+		jp.setLayout(new GridLayout(5,2,1,1));
[…]

### 2016-03-29 src/main/java/examples/jnotepad/Print.java

@@ -1,0 +1,53 @@
+package examples.jnotepad;
+
+
+//import the packages for using the classes in them into the program
+import java.awt.*;
+import java.awt.print.*;
+import javax.swing.*;
+
+/**
+ *A class for creating a printer option.
+ */
+public class Print implements Printable{
+	private Component componentToBePrinted;
+	
+	public static void printComponent(Component c){
+		new Print(c).print();
+	}
+	public Print(Component componentToBePrinted){
+		this.componentToBePrinted = componentToBePrinted;
+	}
+	public void print(){
+		PrinterJob printJob = PrinterJob.getPrinterJob();
+		printJob.setPrintable(this);
+		if(printJob.printDialog())
+		try{
+			printJob.print();
+		}
+		catch(PrinterException pe){
+			System.out.println("Error printing: " + pe);
+		}
+	}
+	public int print(Graphics g, PageFormat pageFormat, int pageIndex){
+		if(pageIndex > 0){
+			return(NO_SUCH_PAGE);
+		}
+		else{
+			Graphics2D g2d = (Graphics2D)g;
+			g2d.translate(pageFormat.getImageableX(), pageFormat.getImageableY());
+			disableDoubleBuffering(componentToBePrinted);
+			componentToBePrinted.paint(g2d);
+			enableDoubleBuffering(componentToBePrinted);
+			return(PAGE_EXISTS);
+		}
+	}
+	public static void disableDoubleBuffering(Component c){
+		RepaintManager currentManager = RepaintManager.currentManager(c);
+		currentManager.setDoubleBufferingEnabled(false);
+	}
+	public static void enableDoubleBuffering(Component c){
+		RepaintManager currentManager = RepaintManager.currentManager(c);
+		currentManager.setDoubleBufferingEnabled(true);
+	}
+}

### 2016-03-29 src/main/java/examples/workout/Main.java

@@ -143,12 +143,12 @@ public class Main extends JFrame {
                 String metabolism = (String)metabolismCombo.getSelectedItem();
                 String experience = (String)experienceCombo.getSelectedItem();
                 int age = 1;
-                float height = 100;
-                float weight = 100;
+                int height = 100;
+                int weight = 100;
                 try {
-                     age = Integer.parseInt(ageTextField.getText().trim());
-                     height = Float.parseFloat(heightTextField.getText().trim());
-                     weight = Float.parseFloat(weightTextField.getText().trim());
+                     age = Integer.parseInt(ageTextField.getText());
+                     height = Integer.parseInt(heightTextField.getText());
+                     weight = Integer.parseInt(weightTextField.getText());
                 } catch (Exception ex) {
                     ;
                 }

### 2016-03-31 doc/paper/james/2016_ASE_ChengLin/TestingGUI.tex
fix bug remove database from catg

\documentclass[blind]{sig-alternate-05-2015}
\usepackage{flushend}
\usepackage{graphicx}
%\usepackage[justification=centering]{caption}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{cite}
\usepackage{listings}
\usepackage[square, comma, sort&compress, numbers]{natbib}
\usepackage{verbatim}
\DeclareMathOperator*{\argmin}{argmin}

\linespread{0.9625}

\clubpenalty = 10000
\widowpenalty = 10000
\displaywidowpenalty = 10000

\newcommand{\commentout}[1]{ }

 \newcommand{\superscript}[1]{\ensuremath{^{\textrm{#1}}}}

 \def\sharedaffiliation{\end{tabular}\newline\begin{tabular}{c}}

 \def\wu{\superscript{*}}
 \def\wg{\superscript{\dag}}
 \def\wdg{\superscript{\ddag}}

\lstset{ %
  language=c,
	backgroundcolor=\color{white},   % choose the background color; you must add \usepackage{color} or \usepackage{xcolor}
	basicstyle=\scriptsize\ttfamily,  % the size of the fonts that are used for the code
	breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
	breaklines=true,                 % sets automatic line breaking
	captionpos=b,                    % sets the caption-position to bottom
	commentstyle=\color{mygreen},    % comment style
	deletekeywords={...},            % if you want to delete keywords from the given language
  escapeinside={(*}{*)},          % if you want to add LaTeX within your code
	extendedchars=true,              % lets you use non-ASCII characters; for 8-bits encodings only, does not work with UTF-8
	frame=single,                    % adds a frame around the code
	keepspaces=true,                 % keeps spaces in text, useful for keeping indentation of code (possibly needs columns=flexible)
	keywordstyle=\color{blue},       % keyword style
	morekeywords={*,...},            % if you want to add more keywords to the set
	numbers=none,                    % where to put the line-numbers; possible values are (none, left, right)
	numbersep=5pt,                   % how far the line-numbers are from the code
	numberstyle=\color{black},       % the style that is used for the line-numbers
	rulecolor=\color{black},         % if not set, the frame-color may be changed on line-breaks within not-black text (e.g. comments (green here))
	showspaces=false,                % show spaces everywhere adding particular underscores; it overrides 'showstringspaces'
	showstringspaces=false,          % underline spaces within strings only
	showtabs=false,                  % show tabs within strings adding particular underscores
	stepnumber=1,                    % the step between two line-numbers. If it's 1, each line will be numbered
	stringstyle=\color{mymauve},     % string literal style
	tabsize=2,                       % sets default tabsize to 2 spaces
	%title=\lstname,                   % show the filename of files included with \lstinputlisting; also try caption instead of title
%	linewidth=0.45\textwidth,
}

%%-----------remove copyright plate-------
\makeatletter
\def\@copyrightspace{\relax}
\makeatother
%%----------------------------------------

\begin{document}

% Copyright
\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}

% DOI
%\doi{10.475/123_4}

% ISBN
%\isbn{123-4567-24-567/08/06}

%Conference
%\conferenceinfo{PLDI '13}{June 16--19, 2013, Seattle, WA, USA}

%\acmPrice{\$15.00}

%
% --- Author Metadata here ---
%\conferenceinfo{WOODSTOCK}{'97 El Paso, Texas USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{GUI Testing as a Service}

\maketitle

\begin{abstract}
  abstract
\end{abstract}

\section{Introduction}\label{section:introduction}

Graphic User Interface(GUI) applications are driven by user events.

Manually testing of GUI is labor intensive.

\texttt{Guitar} \cite{guitar} uses an automatic method to test GUI. It automatically generate event sequences for java GUI applications. But it use built-in concrete value for user inputs. Although it also accepts alternative user inputs, however itself doesn't provide any facility to generate user inputs.

\texttt{Barad} \cite{barad} is a novel GUI testing framework based on symbolic execution. It can obtain data inputs through executing symbolically test cases which are chains of event listener method invocations. It manually created symbolic mirror of java GUI library, so its released source code contains a large symbolic java GUI library. however it lacks necessary documentation, it is very hard to deploy the project, and such a heavy code base might be hard to maintain or error pruning.

\texttt{jfp-awt} \cite{jpfawt} is an extension of the Java PathFinder for java GUI application model checking. It needs the user to specify sets of interaction sequences, for a real GUI application, this might be labor intensive task for testers.

In the paper we present a novel tool \texttt{Guicat} which generate concrete user inputs to cover different program branch. We build our work on top of \texttt{Guitar} and \texttt{Catg} \cite{catg}.

\section{Motivating Example}

\begin{figure}
\label{fig:ex}
  \centering
  \includegraphics[width=50mm,scale=0.5]{./res/ticket.png}
  \caption{GUI for train ticket purchase}
\end{figure}

The GUI shown in Figure~\ref{fig:ex} is an application that we developed to mimic the motivating example used in Barad~\cite{}. calculate the price for a train ticket. The application calculates the price for a train ticket based on the information passed through the GUI. A user must provide a passenger class, name, ID, age level, and begin
and end points. Each passenger class has its own coefficient that is used during the calculation. Each age level has a different
base price depending on the distance to be traveled,
which is the difference between From mile and To mile. Figure~\ref{fig:code} gives the code snippet of the calculation logic.  There are twenty four branches. The
execution of a particular branch depends on the user
input both in the form of data and event sequence (i.e.
selecting a radio button).

This program is used to calculate ticket price according to different properties of the client, such as the class level, or age, or the travel distance. When the \texttt{Buy} button is clicked, the application check the \texttt{Name} and \texttt{ID} input, if the length of the \texttt{Name} string is less or equal than 3, or \texttt{ID} equals to some special string, then the application will display an error message and will not calculate any price. After checking the user information successfully, the application start to calculate the price as follows: read the user class input and set a coefficient for the price, read the user age to go to different pricing branch, read the start and destination input and calculate the distance of traveling, then calculate the price. We can see from the following code snippets that there should be many branches in the code to calculate ticket price for all kinds of clients.

\begin{figure}
\label{fig:code}
\begin{lstlisting}
OnClickCalculatePrice() {
  int coefficient = (classLevel == TicketModel.FIRSTCLASS) ? 2 : 1;
  int dist = to - from;
  assert(dist>0);
  if (ageLevel == Adult) {
    if (dist < 40) {
      price = 100 * coeficient;
    } else if (dist < 45) {
      price = 110 * coeficient;
    } else if (dist < 50) {
      ...
    } 
    ...  
  }
  else if (ageLevel == Senior) {
      ...
  }
 else if (ageLevel == Student) {
        ...
  }
  else if (ageLevel == Child) {
       ... 
   }      
   Price.Display(price);
}

OnClickClassLevel1st(){
  classLevel = FIRSTCLASS;
}

OnClickBuyTicket(){
  assert(price<=maxPrice&&price>=minPrice);
}

OnClickClear(){
   Name=ID=null;
   From=To=0;
   AgeLevel=Adult;
   FirstClass=True;
   2ndClass=False;
 }
\end{lstlisting}
\caption{Code snippet for calculating ticket price}
\end{figure}

Lin, please do the following
1. The code above is just imagination. Please revise it so that our approach can catch some tricky assertion failures.
2. Please give a step-by-step illustration on how our algorithm detects errors in the example

\section{Algorithms}

\begin{algorithm}[htbp]
\caption{TestGeneration(program $GUI$, int $B$, int $S$)}
\label{alg:top}
\begin{algorithmic}[1]
\STATE SET chains = $N_0$.ProduceEventSequence($B$); 
%\STATE SET chains = $N_0$.ChainReduction(chains);
\FORALL {$c \in chains$}
	\STATE $N_i$ = AllocateTask();
	\STATE tests.add($N_i$.SymbolicExecution(c));
\ENDFOR
\end{algorithmic}
\end{algorithm}

Lin, please provide algorithm pseudo-code here and give some explanation.

\section{Implementation}

\subsection{Architecture}

The architecture is described as Figure ~\ref{figure:architecture}

\begin{figure}
  \centering
  \includegraphics[width=100mm,scale=0.5]{./res/archi-hand.jpg}
  \caption{architecture}
  \label{figure:architecture}
\end{figure}

Our goal is to generate user inputs for java GUI applications to achieve high branch and code coverage.

The \textbf{work-flow} is  we let the tester to create a configuration file, indicating which variables should be symbolic.
Based on the configure file we create symbolic variables and symbolic functions which are used to replace the corresponding one in the \textbf{replayed sequences}. We generate replayed sequenses from guitar. Using guitar replayer to replay one event sequence is a replayed sequence. We do the replacement by \texttt{javaagent} using \texttt{ASM} the same way as \texttt{CATG} does. After replacement, we get an instrumented replayed sequence, then we can sent it to catg to do concolic execution. we use shell scripts to glue up modules for the testing process of an AUT.

We handle the problem that for a number input, java GUI framework returns a String to programmer by built in function \textit{getText()}, and the programmer somewhere parse the String to numbers using \textit{Integer.parseInt} or something similar.  Because \texttt{CATG} can't handle this kind of operation, we modify catg to support casting functions like \textit{Integer.parseInt}.

Note that catg requires the tester to set up symbolic variables in source code, and this may be inconvenient when source code is not available. We have automated this process.

The following are details of different modules
\begin{itemize}
  \item{\textbf{configuration file} contains entries of symbolic variable information. Each entry contains four elements separated by comma: widget identifier, widget method, return type, init value. A widget identifier is the \textit{accessibleName} of the java widget, it is set by \textit{setAccessibleName} or \textit{setLabelFor}. Jpf-awt uses the same identifier. (Not certain whether guitar uses the same one or not)}. A widget method is the method which should be replaced by a symbolic one. It is usually a built in function which is used to get user input like \textit{getText, isSelected, getActionCommand}. A return type is the type of this symbolic variable. A feasible return type should be one value in this list: {String,int, long, char, byte, short, boolean}. A init value is the concrete value of the symbolic variable for the symbolic execution to start with.

  \item{\textbf{table of symbolic variables}} is a set of symbolic variables created using the configuration file. It is stored in a \textit{LinkedListedMap} to keep the order of the variables. For each entry in the configuration file, we create exactly one entry in the map whose key is the widget identifier, value is an symbolic entry object. If the return type is String, the symbolic entry object contains a symbolic string variable, if the return type is something else like an int, the symbolic entry object contains a symbolic string variable and a symbolic int variable. To the tester, the symbolic int variable is hidden, the output will write back to the String variable.

  \item{\textbf{supported symbolic functions}} is a collection of manually created functions which are used to replace the corresponding ones in the replayed sequences. For example, we create a static function \textit{SGetText(Object)} for the \textit{getText()} of \textit{javax.swing.TextInput}. A little trick here is to pass the object  to the static function parameter so that the stack frames don't need change.

  \item{\textbf{instrumentation} We use ASM to instrument java bytecode. We replace the function call with a symbolic one if it satisfies the following conditions: 1. the call is from an object which has an widget identifier exists in the configuration file; 2. the function name exists in the configuration file}

    \item{\textbf{parseInt support}}. We add parseInt support to catg. When the symbolic string is transformed to int by \textit{parseInt}, catg doesn't support this function originally, so falls to concrete execution. We modify catg to add this support. When the catg encounters \textit{parseInt}, we check the string. if the string is one in the symbolic table, and there is an int symbolic variable in the same symbolic entry, we use this int symbolic value as the return value of  catg's symbolic call \textit{parseInt}, so catg can continue execute symbolically. We have modified 3 files in catg's originmal source.

\end{itemize}

\section{experiment}
We have tested ticket seller. We user guitar to generate testcase. Each guitar test case we have get up to 13 concrete inputs.

if we set guitar event sequences length to 1, then guitar will genenrate 10 testcases, we can generate 82 testcases.
if we set guitar event sequences length to 2, then guitar will genenrate 89 testcases, we can generate 952 testcases.

\bibliographystyle{unsrt}
\bibliography{paper}

\end{document}

### 2016-03-31 doc/paper/james/2016_ASE_ChengLin/paper.tex
fix bug remove database from catg

--- 2016-03-31 doc/paper/james/2016_ASE_ChengLin/TestingGUI.tex
@@
 base price depending on the distance to be traveled,
-which is the difference between From mile and To mile. Figure~\ref{fig:code} gives the code snippet of the calculation logic.  There are twenty four branches. The
+which is the difference between From mile and To mile.
+Figure~\ref{fig:code} gives the code snippet of the calculation logic.
+There are twenty two branches with conditional statements nested three levels deep.
+The
 execution of a particular branch depends on the user
@@
 When the \texttt{Buy} button is clicked, the application check the \texttt{Name} and \texttt{ID} input, if the length of the \texttt{Name} string is less or equal than 3, or \texttt{ID} equals to some special string, then the application will display an error message and will not calculate any price.
-After checking the user information successfully, the application start to calculate the price as follows: read the user class input and set a coefficient for the price, read the user age to go to different pricing branch, read the start and destination input and calculate the distance of traveling, then calculate the price.
+After checking the user information successfully, the application start to calculate the price as follows: read the user class input and set a coefficient for the price, read the user age to go to different pricing branch, read the start and dest input and calculate the distance of travelling, then calculate the price.
 We can see from the following code snippets that there should be many branches in the code to calculate ticket price for all kinds of clients.
-
 \begin{figure}
@@
 \begin{lstlisting}
-OnClickCalculatePrice() {
+  int maxPrice = 100;
+  int minPrice = 10;
   int coefficient = (classLevel == TicketModel.FIRSTCLASS) ? 2 : 1;
   int dist = to - from;
-  assert(dist>0);
   if (ageLevel == Adult) {
@@
     } else if (dist < 50) {
-      ...
+      price = 120 * coeficient;
+    } else if (dist < 70) {
+      price = 140 * coeficient;
+    } else if (dist < 80) {
+      price = 150 * coeficient;
+    } else if (dist < 85) {
+      price = 155 * coeficient;
+    } else if (dist < 100) {
+      price = 160 * coeficient;
     }
-    ...  
   }
-  else if (ageLevel == Senior) {
-      ...
-  }
- else if (ageLevel == Student) {
-        ...
-  }
-  else if (ageLevel == Child) {
-       ... 
-   }      
-   Price.Display(price);
-}
-
-OnClickClassLevel1st(){
-  classLevel = FIRSTCLASS;
-}
-
-OnClickBuyTicket(){
   assert(price<=maxPrice&&price>=minPrice);
-}
-
-OnClickClear(){
-   Name=ID=null;
-   From=To=0;
-   AgeLevel=Adult;
-   FirstClass=True;
-   2ndClass=False;
- }
 \end{lstlisting}
@@
 
-Lin, please do the following
-1. The code above is just imagination. Please revise it so that our approach can catch some tricky assertion failures.
-2. Please give a step-by-step illustration on how our algorithm detects errors in the example
+One can not claim this kind of applications are well tested until all the branches has been covered during test stage.
 
@@
 \end{algorithm}
-
-Lin, please provide algorithm pseudo-code here and give some explanation.
 

### 2016-03-31 doc/paper/james/2016_ASE_ChengLin/make.sh

@@ -1,0 +1,3 @@
+#! /bin/bash
+paper=paper
+pdflatex $paper && bibtex $paper && pdflatex $paper && evince "paper.pdf"

### 2016-03-31 guicat.sh

@@ -24,21 +24,38 @@ do
     fi
 done
 
+for jar in `ls $libDir`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":"$libDir"/"$jar
+    fi
+done
+
+echo $libDir
+echo $classpath
+
 rm -rf $AUTDIR branches/
 mkdir $AUTDIR
 mkdir branches/
 mkdir $AUTDIR"/testcases"
 
-ripperCmd="java -Dlog4j.configuration=$log4j -cp $classpath edu.umd.cs.guitar.ripper.JFCRipperMain -c $AUT_MAINCLASS -g $guiFile -cf $configurationFile -d 500 -i 2000 -l $logFile"
+./clean.sh
 
+
+cmd="java -cp $classpath guicat.util.PrintAccessbileName $AUT_MAINCLASS"
+eval $cmd > $AUTDIR"/accessbileName.txt"
+
+
+ripperCmd="java -Dlog4j.configuration=$log4j -cp $classpath edu.umd.cs.guitar.ripper.JFCRipperMain -c $AUT_MAINCLASS -g $guiFile -cf $configurationFile -d 500 -i 2000 -l $logFile"
 eval $ripperCmd
 
 gui2efgCmd="java -Dlog4j.configuration=$log4j -cp $classpath  edu.umd.cs.guitar.graph.GUIStructure2GraphConverter -p EFGConverter -g $guiFile -e $efgFile"
 
 eval $gui2efgCmd
 
-#testcaseCmd="java -Dlog4j.configuration=$logFile -cp $classpath  edu.umd.cs.guitar.testcase.TestCaseGenerator -p RandomSequenceLengthCoverage -e $efgFile -l 1 -m 200 -d $AUTTESTCASE"
-testcaseCmd="java -Dlog4j.configuration=$log4j -cp $classpath  edu.umd.cs.guitar.testcase.TestCaseGenerator -p BytecodeAnalysis  -e $efgFile -l 2 -m 200 -d $AUTTESTCASE --scope ./aut/radioButton.jar  --method pair --shared 0"
+testcaseCmd="java -Dlog4j.configuration=$logFile -cp $classpath  edu.umd.cs.guitar.testcase.TestCaseGenerator -p RandomSequenceLengthCoverage -e $efgFile -l 1 -m 200 -d $AUTTESTCASE"
[…]

### 2016-03-31 printAccessibleName.sh

@@ -1,0 +1,15 @@
+#! /usr/bin/env bash
+
+classpath=""
+for jar in `ls aut`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./aut/"$jar
+    fi
+done
+classpath=$classpath":./lib/sym-agent.jar"
+
+cmd="java -cp $classpath guicat.util.PrintAccessbileName $1"
+#echo $cmd
+eval $cmd

### 2016-03-31 src/main/java/database/table/SymbolicTable.java

@@ -1,106 +1,0 @@
-package database.table;
-
-import database.table.internals.ForeignKey;
-import database.table.internals.Row;
-import database.table.internals.Table;
-import database.table.internals.TableIterator;
-import janala.Main;
-import janala.interpreters.OrValue;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 7/2/12
- * Time: 11:47 PM
- */
-public class SymbolicTable {
-
-  public static void insertSymbolicRows(Table table, int n) {
-    insertSymbolicRows(table, n, true);
-  }
-
-  public static void insertSymbolicRowsNoCheck(Table table, int n) {
-    insertSymbolicRows(table, n, false);
-  }
-
-  private static void insertSymbolicRows(Table table, int n, boolean checkConsistency) {
-    int[] types = table.getColumnTypes();
-    boolean[] primaries = table.getPrimaries();
-    String[] columnNames = table.getColumnNames();
-    ForeignKey[] foreignKeys = table.getForeignKeys();
-    for (int i = 0; i < n; i++) {
-      Object[] row = new Object[types.length];
-      System.out.print(table.getName() + " {");
-      for (int j = 0; j < row.length; j++) {
-        if (types[j] == Table.INT) {
-          int x = Main.readInt(i);
-          Main.MakeSymbolic(x);
-          Integer k = new Integer(x);
-          row[j] = k;
-        } else if (types[j] == Table.LONG) {
-          long x = Main.readLong(i);
-          Main.MakeSymbolic(x);
-          Long k = new Long(x);
-          row[j] = k;
-        } else if (types[j] == Table.DATE) {
-          long x = Main.readLong(i + 1);
-          Main.MakeSymbolic(x);
-          Main.Assume(x > 0 ? 1 : 0);
-          java.sql.Date k = new java.sql.Date(x);
-          row[j] = k;
-        } else if (types[j] == Table.TIME) {
-          long x = Main.readLong(i + 1);
-          Main.MakeSymbolic(x);
-          Main.Assume(x > 0 ? 1 : 0);
-          java.sql.Time k = new java.sql.Time(x);
-          row[j] = k;
-        } else if (types[j] == Table.TIMESTAMP) {
-          long x = Main.readLong(i + 1);
-          Main.MakeSymbolic(x);
-          Main.Assume(x > 0 ? 1 : 0);
-          java.sql.Timestamp k = new java.sql.Timestamp(x);
[…]

### 2016-03-31 src/main/java/database/table/commands/SelectCommand.java

@@ -1,138 +1,0 @@
-package database.table.commands;
-
-import database.table.from.From;
-import database.table.groupby.GroupBy;
-import database.table.having.Having;
-import database.table.internals.*;
-import database.table.operations.Operations;
-import database.table.orderby.OrderBy;
-import database.table.select.Select;
-import database.table.where.Where;
-
-import java.util.LinkedList;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class SelectCommand {
-  private Select select;
-  private From from;
-  private Where where;
-  private GroupBy groupBy;
-  private Having having;
-  private OrderBy orderBy;
-  private boolean isDistinct;
-
-  public SelectCommand(
-      Select select,
-      From from,
-      Where where,
-      GroupBy groupBy,
-      Having having,
-      OrderBy orderBy,
-      boolean distinct) {
-    this.select = select;
-    this.from = from;
-    this.where = where;
-    this.groupBy = groupBy;
-    this.having = having;
-    this.orderBy = orderBy;
-    isDistinct = distinct;
-  }
-
-  class Pair {
-    ArrayBasedTuple tuple;
-    Row row;
-
-    Pair(ArrayBasedTuple tuple, Row row) {
-      this.tuple = tuple;
-      this.row = row;
-    }
-  }
-
-  public Table execute() {
-
-    Table[] tables = from.tables();
-    int nTables = tables.length;
-
-    String[] selectAs = select.selectAs();
-    Table ret = TableFactory.create(selectAs);
-
-    TableIterator[] iterators = new TableIterator[nTables];
-    LinkedList<Pair> groups = new LinkedList<Pair>();
-
-    while (hasNext(iterators)) {
-      boolean insert = false;
-      Row[] rows = next(iterators, tables);
-      if (where.where(rows)) {
-        ArrayBasedTuple group = new ArrayBasedTuple(groupBy.groupBy(rows));
-        Row row = null;
-        for (Pair tmp : groups) {
-          if (tmp.tuple.equals(group)) {
-            row = tmp.row;
-            break;
-          }
-        }
-        if (row == null) {
-          row = new Row();
-          insert = true;
-          groups.add(new Pair(group, row));
-        }
-        Operations[] operations = select.select();
-        int i = 0;
-        if (selectAs.length != operations.length) {
-          throw new RuntimeException(
-              "In Select selectAs and select returns different length arrays");
-        }
-        for (String columnName : selectAs) {
[…]

### 2016-03-31 src/main/java/database/table/from/From.java

@@ -1,18 +1,0 @@
-package database.table.from;
-
-import database.table.internals.Table;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class From {
-  private Table[] tables;
-
-  public From(Table[] tables) {
-    this.tables = tables;
-  }
-
-  public Table[] tables() {
-    return tables;
-  }
-}

### 2016-03-31 src/main/java/database/table/groupby/DefaultGroupBy.java

@@ -1,15 +1,0 @@
-package database.table.groupby;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class DefaultGroupBy implements GroupBy {
-  int i = 0;
-
-  public Object[] groupBy(Row[] rows) {
-    i++;
-    return new Object[] {i};
-  }
-}

### 2016-03-31 src/main/java/database/table/groupby/GroupBy.java

@@ -1,10 +1,0 @@
-package database.table.groupby;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public interface GroupBy {
-  public Object[] groupBy(Row[] rows);
-}

### 2016-03-31 src/main/java/database/table/groupby/SimpleGroupBy.java

@@ -1,32 +1,0 @@
-package database.table.groupby;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class SimpleGroupBy implements GroupBy {
-  private String[] columns;
-  private int[] tableIndices;
-
-  public SimpleGroupBy(String[] columns) {
-    this.columns = columns;
-    tableIndices = new int[columns.length];
-    for (int i = 0; i < tableIndices.length; i++) {
-      tableIndices[i] = 0;
-    }
-  }
-
-  public SimpleGroupBy(int[] tableIndices, String[] columns) {
-    this.columns = columns;
-    this.tableIndices = tableIndices;
-  }
-
-  public Object[] groupBy(Row[] rows) {
-    Object[] ret = new Object[columns.length];
-    for (int i = 0; i < ret.length; i++) {
-      ret[i] = rows[tableIndices[i]].get(columns[i]);
-    }
-    return ret;
-  }
-}

### 2016-03-31 src/main/java/database/table/groupby/SingleSetGroupBy.java

@@ -1,12 +1,0 @@
-package database.table.groupby;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class SingleSetGroupBy implements GroupBy {
-  public Object[] groupBy(Row[] rows) {
-    return new Object[] {1};
-  }
-}

### 2016-03-31 src/main/java/database/table/having/Having.java

@@ -1,10 +1,0 @@
-package database.table.having;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public interface Having {
-  public boolean having(Row row);
-}

### 2016-03-31 src/main/java/database/table/having/HavingTrue.java

@@ -1,12 +1,0 @@
-package database.table.having;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class HavingTrue implements Having {
-  public boolean having(Row row) {
-    return true;
-  }
-}

### 2016-03-31 src/main/java/database/table/internals/ArrayBasedTuple.java

@@ -1,44 +1,0 @@
-package database.table.internals;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class ArrayBasedTuple {
-  public Object[] array;
-  private int hc;
-  private boolean isHcInitialized = false;
-
-  public ArrayBasedTuple(Object[] array) {
-    this.array = array;
-  }
-
-  @Override
-  public int hashCode() {
-    if (!isHcInitialized) {
-      hc = 0;
-      for (int i = 0; i < array.length; i++) {
-        Object o = array[i];
-        hc += o.hashCode();
-      }
-      isHcInitialized = true;
-    }
-    return hc;
-  }
-
-  public void invalidateHashCode() {
-    isHcInitialized = false;
-  }
-
-  @Override
-  public boolean equals(Object o) {
-    if (!(o instanceof ArrayBasedTuple)) return false;
-    ArrayBasedTuple other = (ArrayBasedTuple) o;
-    if (array == other.array) return true;
-    if (other.array == null || array == null) return false;
-    if (other.array.length != array.length) return false;
-    for (int i = 0; i < array.length; i++) {
-      if (!array[i].equals(other.array[i])) return false;
-    }
-    return true;
-  }
-}

### 2016-03-31 src/main/java/database/table/internals/ConsistencyChecker.java

@@ -1,162 +1,0 @@
-package database.table.internals;
-
-import janala.Main;
-import janala.interpreters.OrValue;
-
-public class ConsistencyChecker {
-
-  public static void checkRow(Table table, Row row) {
-    boolean[] primaries = table.getPrimaries();
-    boolean[] uniques = table.getUniques();
-    boolean[] nonnulls = table.getNonNulls();
-    String[] columnNames = table.getColumnNames();
-    ForeignKey[] foreignKeys = table.getForeignKeys();
-
-    int cnt = 0;
-    for (int j = 0; j < columnNames.length; j++) {
-      if (primaries != null && primaries[j]) cnt++;
-    }
-    if (cnt > 0) {
-      Object[] thisPrimary = new Object[cnt];
-      int i = 0;
-      for (int j = 0; j < columnNames.length; j++) {
-        if (primaries != null && primaries[j]) {
-          thisPrimary[i] = row.get(columnNames[j]);
-          assert thisPrimary[i] != null;
-          i++;
-        }
-      }
-      ArrayBasedTuple thisArray = new ArrayBasedTuple(thisPrimary);
-      TableIterator iter = table.iterator();
-      while (iter.hasNext()) {
-        Row otherRow = iter.next();
-        if (row != otherRow) {
-          Object[] otherPrimary = new Object[cnt];
-          i = 0;
-          for (int j = 0; j < columnNames.length; j++) {
-            if (primaries != null && primaries[j]) {
-              otherPrimary[i] = otherRow.get(columnNames[j]);
-              assert otherPrimary[i] != null;
-              i++;
-            }
-          }
-          ArrayBasedTuple otherArray = new ArrayBasedTuple(otherPrimary);
-          assert (!thisArray.equals(otherArray));
-        }
-      }
-    }
-    for (int j = 0; j < columnNames.length; j++) {
-      if (uniques != null && uniques[j]) {
-        Object value = row.get(columnNames[j]);
-        assert value != null;
-        TableIterator iter = table.iterator();
-        while (iter.hasNext()) {
-          Row otherRow = iter.next();
-          if (row != otherRow) assert (!value.equals(otherRow.get(columnNames[j])));
-        }
-      }
-      if (nonnulls != null && nonnulls[j]) {
-        Object value = row.get(columnNames[j]);
-        assert value != null;
-      }
-    }
-    for (int j = 0; j < columnNames.length; j++) {
-      if (foreignKeys != null && foreignKeys[j] != null) {
[…]

### 2016-03-31 src/main/java/database/table/internals/ForeignKey.java

@@ -1,16 +1,0 @@
-package database.table.internals;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 7/9/12
- * Time: 12:40 PM
- */
-public class ForeignKey {
-  public Table table;
-  public String key;
-
-  public ForeignKey(Table table, String key) {
-    this.table = table;
-    this.key = key;
-  }
-}

### 2016-03-31 src/main/java/database/table/internals/Predicate.java

@@ -1,8 +1,0 @@
-package database.table.internals;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public interface Predicate {
-  public boolean predicate(Object o1, Object o2);
-}

### 2016-03-31 src/main/java/database/table/internals/ResultSetImpl.java

@@ -1,794 +1,0 @@
-package database.table.internals;
-
-import java.io.InputStream;
-import java.io.Reader;
-import java.math.BigDecimal;
-import java.net.URL;
-import java.sql.*;
-import java.util.Calendar;
-import java.util.Map;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 7/2/12
- * Time: 1:04 PM
- */
-public class ResultSetImpl implements ResultSet {
-  TableIterator iterator;
-  Row currentRow;
-
-  public ResultSetImpl(TableIterator iterator) {
-    this.iterator = iterator;
-  }
-
-  public boolean next() throws SQLException {
-    if (iterator.hasNext()) {
-      currentRow = iterator.next();
-      return true;
-    }
-    return false;
-  }
-
-  public void close() throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public boolean wasNull() throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public String getString(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public boolean getBoolean(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public byte getByte(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public short getShort(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public int getInt(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public long getLong(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public float getFloat(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public double getDouble(int i) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public BigDecimal getBigDecimal(int i, int i1) throws SQLException {
-    throw new RuntimeException("Unimplemented method in ResultSetImpl");
-  }
-
-  public byte[] getBytes(int i) throws SQLException {
[…]

### 2016-03-31 src/main/java/database/table/internals/Row.java

@@ -1,29 +1,0 @@
-package database.table.internals;
-
-import java.util.TreeMap;
-import java.util.TreeSet;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/12/12
- * Time: 10:52 AM
- */
-public class Row extends TreeMap<String, Object> {
-  @Override
-  public boolean equals(Object o) {
-    if (!(o instanceof TreeMap)) {
-      return false;
-    }
-    TreeMap<String, Object> other = (TreeMap<String, Object>) o;
-    TreeSet<String> tmp = new TreeSet<String>(keySet());
-    tmp.addAll(other.keySet());
-    for (String key : tmp) {
-      Object value1 = get(key);
-      Object value2 = other.get(key);
-      if (value1 == null && value2 != null) return false;
-      if (value2 == null && value1 != null) return false;
-      if (value1 != value2 && !value1.equals(value2)) return false;
-    }
-    return true;
-  }
-}

### 2016-03-31 src/main/java/database/table/internals/Table.java

@@ -1,68 +1,0 @@
-package database.table.internals;
-
-import database.table.orderby.OrderBy;
-import database.table.where.Where;
-
-import java.sql.ResultSet;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 7/2/12
- * Time: 12:32 PM
- */
-public interface Table {
-  final public static int INT = 1;
-  final public static int STRING = 2;
-  final public static int LONG = 3;
-  final public static int DATE = 4;
-  final public static int TIME = 5;
-  final public static int TIMESTAMP = 6;
-  int NONE = 0;
-  int PRIMARY = 1;
-  int UNIQUE = 2;
-  int NONNULL = 4;
-
-  public void insert(Row row);
-
-  public void insert(String[] columns, Object[] values);
-
-  public void insert(Object[] values);
-
-  public void insertNoCheck(Object[] row);
-
-  public TableIterator iterator();
-
-  public int delete(Where where);
-
-  public int update(Where where);
-
-  public Table select(Where where, String[][] selectColumns, Table[] fromOther);
-
-  public ResultSet getResultSet();
-
-  public String getName();
-
-  public String[] getColumnNames();
-
-  public int[] getColumnTypes();
-
-  public boolean[] getPrimaries();
-
-  public boolean[] getUniques();
-
-  public boolean[] getNonNulls();
-
-  public ForeignKey[] getForeignKeys();
-
-  public void orderBy(OrderBy orderBy);
-
-  public int size();
-
-  public Object value();
-
-  public boolean in(Object o);
-
-  public boolean any(Object o, Predicate p);
-
-  public void setForeignKeys(ForeignKey[] fkeys);
-}

### 2016-03-31 src/main/java/database/table/internals/TableFactory.java

@@ -1,36 +1,0 @@
-package database.table.internals;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 7/2/12
- * Time: 12:33 PM
- */
-public class TableFactory {
-  private static int anonymousTableCount = 0;
-
-  public static Table create(String[] columnNames) {
-    anonymousTableCount++;
-    return new TableImpl("InternalTable" + anonymousTableCount, columnNames);
-  }
-
-  public static Table create(
-      String name,
-      String[] columnNames,
-      int[] columnTypes,
-      int[] attributes,
-      ForeignKey[] foreignKeys) {
-    assert (columnNames.length == columnTypes.length
-        && columnNames.length == attributes.length
-        && columnNames.length == foreignKeys.length);
-    boolean[] primaries = new boolean[attributes.length];
-    boolean[] uniques = new boolean[attributes.length];
-    boolean[] nonulls = new boolean[attributes.length];
-    for (int i = 0; i < attributes.length; i++) {
-      int attribute = attributes[i];
-      primaries[i] = (attribute & Table.PRIMARY) != 0;
-      uniques[i] = (attribute & Table.UNIQUE) != 0;
-      nonulls[i] = (attribute & Table.NONNULL) != 0;
-    }
-    return new TableImpl(name, columnNames, columnTypes, primaries, uniques, nonulls, foreignKeys);
-  }
-}

### 2016-03-31 src/main/java/database/table/internals/TableImpl.java

@@ -1,278 +1,0 @@
-package database.table.internals;
-
-import database.table.orderby.OrderBy;
-import database.table.where.Where;
-
-import java.sql.ResultSet;
-import java.util.*;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 7/2/12
- * Time: 10:18 AM
- */
-public class TableImpl implements Table {
-  private String name;
-  private String[] columnNames;
-  private int[] columnTypes;
-  private boolean[] isPrimary;
-  private boolean[] isUnique;
-  private boolean[] isNonNull;
-  private ForeignKey[] foreignKeys;
-  private List<Row> rows;
-
-  public TableImpl(String name, String[] columnNames) {
-    this.name = name;
-    this.columnNames = columnNames;
-    rows = new LinkedList<Row>();
-  }
-
-  public TableImpl(
-      String name,
-      String[] columnNames,
-      int[] columnTypes,
-      boolean[] primary,
-      boolean[] unique,
-      boolean[] nonNull,
-      ForeignKey[] foreignKeys) {
-    this.name = name;
-    this.columnNames = columnNames;
-    this.columnTypes = columnTypes;
-    this.foreignKeys = foreignKeys;
-    this.isPrimary = primary;
-    this.isUnique = unique;
-    this.isNonNull = nonNull;
-    rows = new LinkedList<Row>();
-  }
-
-  public void insert(Row row) {
-    ConsistencyChecker.checkRow(this, row);
-    rows.add(row);
-  }
-
-  public void insert(String[] columns, Object[] values) {
-    assert (columns.length == values.length);
-    Row row = new Row();
-    for (int i = 0; i < columns.length; i++) {
-      String column = columns[i];
-      row.put(column, values[i]);
-    }
-    ConsistencyChecker.checkRow(this, row);
-    rows.add(row);
-  }
-
-  public void insert(Object[] values) {
-    assert (columnNames.length == values.length);
-    Row row = new Row();
-    for (int i = 0; i < columnNames.length; i++) {
-      String column = columnNames[i];
-      row.put(column, values[i]);
-    }
-    ConsistencyChecker.checkRow(this, row);
-    rows.add(row);
-  }
-
-  public void insertNoCheck(Object[] values) {
-    assert (columnNames.length == values.length);
-    Row row = new Row();
-    for (int i = 0; i < columnNames.length; i++) {
-      String column = columnNames[i];
-      row.put(column, values[i]);
-    }
-    rows.add(row);
[…]

### 2016-03-31 src/main/java/database/table/internals/TableIterator.java

@@ -1,52 +1,0 @@
-package database.table.internals;
-
-import java.util.ListIterator;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/12/12
- * Time: 11:06 AM
- */
-public class TableIterator {
-  private ListIterator<Row> iter;
-
-  public TableIterator(ListIterator<Row> iter) {
-    this.iter = iter;
-  }
-
-  public boolean hasNext() {
-    return iter.hasNext();
-  }
-
-  public Row next() {
-    return iter.next();
-  }
-
-  public boolean hasPrevious() {
-    return iter.hasPrevious();
-  }
-
-  public Row previous() {
-    return iter.previous();
-  }
-
-  public int nextIndex() {
-    return iter.nextIndex();
-  }
-
-  public int previousIndex() {
-    return iter.previousIndex();
-  }
-
-  public void remove() {
-    iter.remove();
-  }
-
-  public void set(Row row) {
-    iter.set(row);
-  }
-
-  public void add(Row row) {
-    iter.add(row);
-  }
-}

### 2016-03-31 src/main/java/database/table/operations/CountOperation.java

@@ -1,45 +1,0 @@
-package database.table.operations;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/22/12
- * Time: 2:00 AM
- */
-public class CountOperation extends StandardOperation {
-  final private static Object dummy = new Object();
-
-  public CountOperation(int tableIndex, String columnName) {
-    super(tableIndex, columnName);
-  }
-
-  public CountOperation(String columnName) {
-    super(columnName);
-  }
-
-  public CountOperation() {
-    super(null);
-  }
-
-  public Object apply(Object old, Row[] rows) {
-    Object nu;
-    if (columnName == null) nu = dummy;
-    else nu = rows[tableIndex].get(columnName);
-    if (old == null && nu == null) return 0;
-    if (old == null) return 1;
-    if (nu == null) return old;
-    return (Integer) old + 1;
-  }
-
-  @Override
-  protected Object operation(Object aggregate, Object current) {
-    throw new RuntimeException("Should not be called.");
-  }
-
-  @Override
-  public String name() {
-    if (columnName == null) return "COUNT(*)";
-    else return "COUNT(" + columnName + ")";
-  }
-}

### 2016-03-31 src/main/java/database/table/operations/IdentityOperation.java

@@ -1,25 +1,0 @@
-package database.table.operations;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class IdentityOperation extends StandardOperation {
-
-  public IdentityOperation(int tableIndex, String columnName) {
-    super(tableIndex, columnName);
-  }
-
-  public IdentityOperation(String columnName) {
-    super(columnName);
-  }
-
-  @Override
-  protected Object operation(Object aggregate, Object current) {
-    return aggregate;
-  }
-
-  @Override
-  public String name() {
-    return columnName;
-  }
-}

### 2016-03-31 src/main/java/database/table/operations/MaxOperation.java

@@ -1,26 +1,0 @@
-package database.table.operations;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class MaxOperation extends StandardOperation {
-  public MaxOperation(int tableIndex, String columnName) {
-    super(tableIndex, columnName);
-  }
-
-  public MaxOperation(String columnName) {
-    super(columnName);
-  }
-
-  @Override
-  protected Object operation(Object aggregate, Object current) {
-    Comparable nu = (Comparable) current;
-    Comparable ol = (Comparable) aggregate;
-    return nu.compareTo(ol) > 0 ? nu : ol;
-  }
-
-  @Override
-  public String name() {
-    return "MAX(" + columnName + ")";
-  }
-}

### 2016-03-31 src/main/java/database/table/operations/MinOperation.java

@@ -1,27 +1,0 @@
-package database.table.operations;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class MinOperation extends StandardOperation {
-
-  public MinOperation(int tableIndex, String columnName) {
-    super(tableIndex, columnName);
-  }
-
-  public MinOperation(String columnName) {
-    super(columnName);
-  }
-
-  @Override
-  protected Object operation(Object aggregate, Object current) {
-    Comparable nu = (Comparable) current;
-    Comparable ol = (Comparable) aggregate;
-    return nu.compareTo(ol) < 0 ? nu : ol;
-  }
-
-  @Override
-  public String name() {
-    return "MIN(" + columnName + ")";
-  }
-}

### 2016-03-31 src/main/java/database/table/operations/Operations.java

@@ -1,10 +1,0 @@
-package database.table.operations;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public interface Operations {
-  public Object apply(Object old, Row[] rows);
-}

### 2016-03-31 src/main/java/database/table/operations/StandardOperation.java

@@ -1,34 +1,0 @@
-package database.table.operations;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/22/12
- * Time: 1:31 AM
- */
-public abstract class StandardOperation implements Operations {
-  public int tableIndex;
-  public String columnName;
-
-  public StandardOperation(int tableIndex, String columnName) {
-    this.tableIndex = tableIndex;
-    this.columnName = columnName;
-  }
-
-  public StandardOperation(String columnName) {
-    this.tableIndex = 0;
-    this.columnName = columnName;
-  }
-
-  public Object apply(Object old, Row[] rows) {
-    Object nu = rows[tableIndex].get(columnName);
-    if (old == null) return nu;
-    if (nu == null) return old;
-    return operation(old, nu);
-  }
-
-  protected abstract Object operation(Object aggregate, Object current);
-
-  public abstract String name();
-}

### 2016-03-31 src/main/java/database/table/operations/SumOperation.java

@@ -1,29 +1,0 @@
-package database.table.operations;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/22/12
- * Time: 1:57 AM
- */
-public class SumOperation extends StandardOperation {
-
-  public SumOperation(int tableIndex, String columnName) {
-    super(tableIndex, columnName);
-  }
-
-  public SumOperation(String columnName) {
-    super(columnName);
-  }
-
-  @Override
-  protected Object operation(Object aggregate, Object current) {
-    Integer nu = (Integer) current;
-    Integer ol = (Integer) aggregate;
-    return nu + ol;
-  }
-
-  @Override
-  public String name() {
-    return "SUM(" + columnName + ")";
-  }
-}

### 2016-03-31 src/main/java/database/table/orderby/OrderBy.java

@@ -1,12 +1,0 @@
-package database.table.orderby;
-
-import database.table.internals.Row;
-
-import java.util.Comparator;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public interface OrderBy {
-  public Comparator<Row> getComparator();
-}

### 2016-03-31 src/main/java/database/table/orderby/SimpleOrderBy.java

@@ -1,37 +1,0 @@
-package database.table.orderby;
-
-import database.table.internals.Row;
-
-import java.util.Comparator;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class SimpleOrderBy implements OrderBy {
-  Comparator comp;
-  String[] columns;
-  boolean isAscending;
-
-  public SimpleOrderBy(String[] columnNames, boolean ascending) {
-    this.columns = columnNames;
-    isAscending = ascending;
-    comp =
-        new Comparator<Row>() {
-          public int compare(Row r1, Row r2) {
-            for (int i = 0; i < columns.length; i++) {
-              String cname = columns[i];
-              int cmp = ((Comparable) r1.get(cname)).compareTo((Comparable) r2.get(cname));
-              if (cmp != 0) {
-                if (!isAscending) return 0 - cmp;
-                else return cmp;
-              }
-            }
-            return 0;
-          }
-        };
-  }
-
-  public Comparator<Row> getComparator() {
-    return comp;
-  }
-}

### 2016-03-31 src/main/java/database/table/select/OperationMultiTableSelect.java

@@ -1,14 +1,0 @@
-package database.table.select;
-
-import database.table.operations.StandardOperation;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class OperationMultiTableSelect extends StandardOperationsSelect {
-
-  public OperationMultiTableSelect(String[] columnNames, StandardOperation[] operations) {
-    this.operations = operations;
-    this.columns = columnNames;
-  }
-}

### 2016-03-31 src/main/java/database/table/select/OperationSingleTableSelect.java

@@ -1,20 +1,0 @@
-package database.table.select;
-
-import database.table.operations.StandardOperation;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/22/12
- * Time: 1:34 AM
- */
-public class OperationSingleTableSelect extends StandardOperationsSelect {
-
-  public OperationSingleTableSelect(StandardOperation[] operations) {
-    this.operations = operations;
-    this.columns = new String[operations.length];
-    for (int i = 0; i < operations.length; i++) {
-      StandardOperation operation = operations[i];
-      columns[i] = operation.name();
-    }
-  }
-}

### 2016-03-31 src/main/java/database/table/select/Select.java

@@ -1,14 +1,0 @@
-package database.table.select;
-
-import database.table.operations.Operations;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/20/12
- * Time: 12:44 PM
- */
-public interface Select {
-  public String[] selectAs();
-
-  public Operations[] select();
-}

### 2016-03-31 src/main/java/database/table/select/SelectStar.java

@@ -1,14 +1,0 @@
-package database.table.select;
-
-import database.table.internals.Table;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 8/27/12
- * Time: 8:35 AM
- */
-public class SelectStar extends SimpleSingleTableSelect {
-  public SelectStar(Table table) {
-    super(table.getColumnNames());
-  }
-}

### 2016-03-31 src/main/java/database/table/select/SimpleMultiTableSelect.java

@@ -1,21 +1,0 @@
-package database.table.select;
-
-import database.table.operations.IdentityOperation;
-import database.table.operations.StandardOperation;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class SimpleMultiTableSelect extends StandardOperationsSelect {
-
-  public SimpleMultiTableSelect(String[] target, int[] tableIndices, String[] source) {
-    if (target.length != tableIndices.length || target.length != source.length) {
-      throw new RuntimeException("target, tableIndices, source must have same lengths");
-    }
-    this.columns = target;
-    this.operations = new StandardOperation[source.length];
-    for (int i = 0; i < source.length; i++) {
-      operations[i] = new IdentityOperation(tableIndices[i], source[i]);
-    }
-  }
-}

### 2016-03-31 src/main/java/database/table/select/SimpleSingleTableSelect.java

@@ -1,18 +1,0 @@
-package database.table.select;
-
-import database.table.operations.IdentityOperation;
-import database.table.operations.StandardOperation;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class SimpleSingleTableSelect extends StandardOperationsSelect {
-
-  public SimpleSingleTableSelect(String[] columns) {
-    this.columns = columns;
-    this.operations = new StandardOperation[columns.length];
-    for (int i = 0; i < columns.length; i++) {
-      this.operations[i] = new IdentityOperation(columns[i]);
-    }
-  }
-}

### 2016-03-31 src/main/java/database/table/select/StandardOperationsSelect.java

@@ -1,20 +1,0 @@
-package database.table.select;
-
-import database.table.operations.Operations;
-import database.table.operations.StandardOperation;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class StandardOperationsSelect implements Select {
-  String[] columns;
-  StandardOperation[] operations;
-
-  public String[] selectAs() {
-    return columns;
-  }
-
-  public Operations[] select() {
-    return operations;
-  }
-}

### 2016-03-31 src/main/java/database/table/where/Where.java

@@ -1,16 +1,0 @@
-package database.table.where;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- * Date: 7/2/12
- * Time: 10:42 AM
- */
-public abstract class Where {
-  public boolean modify(Row row) {
-    throw new RuntimeException("Unimplemented modify in Where class");
-  }
-
-  public abstract boolean where(Row[] rows);
-}

### 2016-03-31 src/main/java/database/table/where/WhereTrue.java

@@ -1,13 +1,0 @@
-package database.table.where;
-
-import database.table.internals.Row;
-
-/**
- * Author: Koushik Sen (ksen@cs.berkeley.edu)
- */
-public class WhereTrue extends Where {
-  @Override
-  public boolean where(Row[] rows) {
-    return true;
-  }
-}

### 2016-03-31 src/main/java/examples/ticket/BaradTicket.java

@@ -173,12 +173,26 @@ public class BaradTicket {
                     System.out.println( ticketModel.from  < 1 ? "" : "");
                     */
 
+
+                    //ticketModel.computePrice();
+                   // infoField.setText(String.valueOf(ticketModel.price));
+                    /*
+                    if (ticketModel.to - ticketModel.from  < 40 ) {
+                        System.out.println("less");
+
+                    }else {
+                        System.out.println("more");
+                    }
+                    */
+
+
                     if(ticketModel.checkModel()) {
                         ticketModel.computePrice();
                         infoField.setText(String.valueOf(ticketModel.price));
                     } else {
                         infoField.setText(ticketModel.msg);
                     }
+
                 }
             });
 

### 2016-03-31 src/main/java/examples/ticket/Ticket.java

@@ -18,16 +18,16 @@ public class Ticket extends JFrame {
         JLabel hello = new JLabel("Ticket Seller", JLabel.CENTER);
         hello.setFont(new Font("Default", Font.BOLD, 18));
         contentPane.add(hello, new GridBagConstraints(0, 0, 2, 1, 0, 0,
-                                                      GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
+                GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
 
 
         JLabel name = new JLabel("Enter your name:", JLabel.RIGHT);
         contentPane.add(name, new GridBagConstraints(0, 1, 1, 1, 0, 0,
-                                                     GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
+                GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
 
         final JTextField nameInput = new JTextField();
         contentPane.add(nameInput, new GridBagConstraints(1, 1, 1, 1, 0, 0,
-                                                          GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
+                GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
 
         name.setLabelFor(nameInput);
         /*
@@ -40,11 +40,11 @@ public class Ticket extends JFrame {
 
         JLabel age = new JLabel("Enter your age:", JLabel.RIGHT);
         contentPane.add(age, new GridBagConstraints(0, 3, 1, 1, 0, 0,
-                                                    GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
+                GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
 
         final JTextField ageInput = new JTextField();
         contentPane.add(ageInput, new GridBagConstraints(1, 3, 1, 1, 0, 0,
-                                                         GridBagConstraints.CENTER, GridBagConstraints.NONE, new Insets(0, 0, 0, 0), 0, 0));
[…]

### 2016-03-31 src/main/java/examples/ticket/TicketModel.java

@@ -50,7 +50,7 @@ public class TicketModel {
         if (ageLevel == 1) {
             if (dist < 40) {
                 price = 100 * coeficient;
-            } else if (dist < 45) {
+            } /* else  if (dist < 45) {
                 price = 110 * coeficient;
             } else if (dist < 50) {
                 price = 120 * coeficient;
@@ -62,13 +62,13 @@ public class TicketModel {
                 price = 155 * coeficient;
             } else if (dist < 100) {
                 price = 160 * coeficient;
-            }
+            } */
         }
 
         if (ageLevel == 2) {
             if (dist < 40) {
                 price = 120 * coeficient;
-            } else if (dist < 45) {
+            } /* else if (dist < 45) {
                 price = 130 * coeficient;
             } else if (dist < 50) {
                 price = 140 * coeficient;
@@ -80,7 +80,7 @@ public class TicketModel {
                 price = 175 * coeficient;
             } else if (dist < 100) {
                 price = 180 * coeficient;
-            }
+            } */
         }
     }
 }

### 2016-03-31 src/main/java/guicat/testcase/Generator.java

@@ -27,6 +27,7 @@ public class Generator {
     synchronized public static Map<String, String> getGUINameIDBindMap(String guiFile) {
         if (bind == null)
             bind = getNameIDMap(guiFile);
+        System.out.println("_____" + bind.toString());
         return bind;
     }
 
@@ -43,19 +44,19 @@ public class Generator {
         String title = "";
         String ID = "";
         String key = "";
+        String value = "";
+        Map<String, String> tmp = new HashMap<>();
         Map<String, String> ret = new HashMap<String, String>();
         try {
             File inputFile = new File(guiFile);
-            DocumentBuilderFactory dbFactory
-                    = DocumentBuilderFactory.newInstance();
+            DocumentBuilderFactory dbFactory = DocumentBuilderFactory.newInstance();
             DocumentBuilder dBuilder = dbFactory.newDocumentBuilder();
             Document doc = dBuilder.parse(inputFile);
             doc.getDocumentElement().normalize();
-            System.out.println("Root element :"
-                    + doc.getDocumentElement().getNodeName());
             NodeList aList = doc.getElementsByTagName("Attributes");
             System.out.println("----------------------------");
             for (int temp = 0; temp < aList.getLength(); temp++) {
+                tmp.clear();
                 Node aNode = aList.item(temp);  //Attributes
                 //   System.out.println("\nCurrent Element :" + nNode.getNodeName());
                 NodeList pList = aNode.getChildNodes();
@@ -71,22 +72,15 @@ public class Generator {
                                 key = element.getTextContent();
                             }
                             if (element.getNodeName().trim().equals("Value")) {
-                                if (key.equals("ID")) {
-                                    ID = element.getTextContent();
-                                }
-                                if (key.equals("Title")) {
-                                    title = element.getTextContent();
-                                }
+                                value = element.getTextContent();
                             }
-                        } else {
-                            //  throw new Exception("parse gui fail!");
                         }
                     }
-                    if (!title.isEmpty() && ID.startsWith("w")) {
-                        ret.put(title, ID);
-                        key = "";
-                        title = "";
-                        ID = "";
+                    tmp.put(key, value);
+                }
+                if (tmp.containsKey("ID") && tmp.containsKey("Title") && tmp.containsKey("Class")  ){
+                    if ( ! tmp.get("Class").equals("javax.swing.JLabel")) {
[…]

### 2016-03-31 src/main/java/guicat/util/PrintAccessbileName.java

@@ -1,0 +1,82 @@
+package guicat.util;
+
+
+import javax.accessibility.AccessibleContext;
+import java.awt.*;
+import java.lang.reflect.Method;
+
+public class PrintAccessbileName {
+    static String indent = "";
+    static int  level = 1;
+
+
+    public static void main(String[] args) {
+
+        if (args.length < 1) {
+            System.out.println("please provide program name");
+        }
+        String autMain = args[0];
+
+
+        try {
+            Class c = Class.forName(autMain);
+            Method m = c.getMethod("main", String[].class);
+            m.invoke(null, new Object[]{null});
+        } catch (Exception e) {
+            e.printStackTrace();
+        }
+
+
+        try {
+            Thread.sleep(2000);
+        } catch (InterruptedException e) {
+            e.printStackTrace();
+        }
+
+        Frame[] frames = null;
+        frames = Frame.getFrames();
+
+        //mot work, frame comes out, but accessible context doesn't come out
+//        int i = 0;
+//        while ( (frames = Frame.getFrames()) == null ) {
+//            System.out.println(frames.toString());
+//        };
+
+        int i = 1;
+        for (Frame frame : frames) {
+            System.out.println("====== accessibleName for frame: " + i++ + "=============");
+            dumpInfo(frame.getAccessibleContext());
+        }
+
+        for (Frame frame : frames) {
+            frame.dispose();
+        }
+    }
+
+
+
+
+    public static void dumpInfo(AccessibleContext ac) {
+        /*
+        if( ac.getAccessibleEditableText() != null) {
+        System.out.println("------ level " + level++);
+        System.out.println("    " + ac.getAccessibleName());
+        System.out.println("    " + ac.getAccessibleEditableText());
+        System.out.println("Description = " + ac.getAccessibleDescription());
+        }
+        */
+        System.out.println(level + indent + ac.getAccessibleName());
+        int nChildren = ac.getAccessibleChildrenCount();
+        indent += "    ";
+        level++;
+
+        for (int i = 0; i < nChildren; i++){
+            dumpInfo(ac.getAccessibleChild(i).getAccessibleContext());
+            level--;
+            indent = indent.substring(0, indent.length()-4);
+        }
+    }
+
+
+
+}

### 2016-04-01 replay-a-test-case.sh
add aut some jars

@@ -1,0 +1,39 @@
+#! /usr/bin/env bash
+
+
+. ./conf/barad-ticket/barad-ticket.conf
+
+testcase_id=t_e1471183336
+
+classpath="."
+for jar in `ls lib`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./lib/"$jar
+    fi
+done
+
+for jar in `ls aut`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./aut/"$jar
+    fi
+done
+
+for jar in `ls $libDir`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":"$libDir"/"$jar
+    fi
+done
+
+echo $libDir
+echo $classpath
+
+cmd="java  -Dlog4j.configuration=$log4j -cp $classpath edu.umd.cs.guitar.replayer.JFCReplayerMain -c $AUT_MAINCLASS -g $guiFile -e $efgFile -t $AUTDIR/testcases/$testcase_id.tst -i 2000 -d 200 -l $AUTDIR/logs/$testcase_id.log -gs $AUTDIR/states/$testcase_id.sta -cf $configurationFile -ts"
+
+echo $cmd
+eval $cmd

### 2016-04-01 src/main/java/examples/test/Replay.java

@@ -1,0 +1,14 @@
+package examples.test;
+
+import edu.umd.cs.guitar.event.JFCSelectionHandler;
+import edu.umd.cs.guitar.replayer.JFCReplayerMain;
+
+/**
+ * Created by oliver on 31/03/16.
+ */
+public class Replay {
+    public static void main(String[] args) {
+        String[] ss = {"-c", "examples.ticket.BaradTicket", "-g", "log/barad-ticket/barad-ticket.GUI", "-e", "log/barad-ticket/barad-ticket.EFG", "-t", "log/barad-ticket/testcases/t_e1471183336.tst", "-i", "2000", "-d", "200", "-l", "log/barad-ticket/logs/t_e1471183336.log", "-gs", "log/barad-ticket/states/t_e1471183336.sta", "-cf", "./conf/barad-ticket/configuration.xml"};
+        JFCReplayerMain.main(ss);
+    }
+}

### 2016-04-01 src/main/java/examples/ticket/BaradTicket.java

@@ -20,6 +20,7 @@ public class BaradTicket {
     JTextField fromInput;
     JTextField toInput;
     JComboBox ageCombo;
+    JCheckBox aCheckBox;
 
 
     private TicketModel ticketModel;
@@ -154,6 +155,21 @@ public class BaradTicket {
         }
 
         {
+            JLabel checkLabel = new JLabel("ACheckBox");
+            gbc.gridx = 0;
+            gbc.gridy = 8;
+            contentPane.add(checkLabel, gbc);
+
+            aCheckBox = new JCheckBox("MyCheckBox");
+            gbc.gridx = 1;
+            gbc.gridy = 8;
+            contentPane.add(aCheckBox, gbc);
+            checkLabel.setLabelFor(aCheckBox);
+            aCheckBox.setSelected(true);
+
+        }
+
+        {
             buyButton.addActionListener(new ActionListener() {
                 public void actionPerformed(ActionEvent e) {
                     ticketModel.name = nameInput.getText();
@@ -162,11 +178,22 @@ public class BaradTicket {
                     ticketModel.to = Integer.parseInt(toInput.getText());
 
                     String tmpAgeString = (String)ageCombo.getSelectedItem();
-                    if (tmpAgeString.equals("Child"))
+                    if (tmpAgeString.equals("Child")) {
                         ticketModel.ageLevel = 1;
-                    if (tmpAgeString.equals("Adult"))
+                        infoField.setText("Child");
+                    }
+                    if (tmpAgeString.equals("Adult")) {
                         ticketModel.ageLevel = 2;
+                        infoField.setText("Adult");
+                    }
 
+                    /*
+                    if (aCheckBox.isSelected()) {
+                        infoField.setText("checked");
+                    } else {
+                        infoField.setText("unchecked!");
+                    }
+                    */
                     /*
                     System.out.println( ticketModel.name.equals("oliver")  ? "" : "");
                     System.out.println( ticketModel.to  >= 5 ? "" : "");
@@ -185,14 +212,14 @@ public class BaradTicket {
                     }
                     */
 
-
+/*
                     if(ticketModel.checkModel()) {
                         ticketModel.computePrice();
                         infoField.setText(String.valueOf(ticketModel.price));
                     } else {
                         infoField.setText(ticketModel.msg);
                     }
-
+*/
                 }
             });
 

### 2016-04-01 src/main/java/examples/ticket/TicketModel.java

@@ -45,7 +45,12 @@ public class TicketModel {
 
     public void computePrice() {
 
-        int coeficient = (classLevel == TicketModel.FIRSTCLASS) ? 1 : 2;
+        int coeficient = 0;
+        if (classLevel == TicketModel.FIRSTCLASS) {
+            coeficient = 1;
+        } else {
+            coeficient = 2;
+        }
         int dist = to - from;
         if (ageLevel == 1) {
             if (dist < 40) {

### 2016-04-01 src/main/java/guicat/SymAgent.java

@@ -51,8 +51,10 @@ public class SymAgent implements ClassFileTransformer {
                     if (in1a.getOpcode() == Opcodes.GETFIELD) {
                         FieldInsnNode in1b = (FieldInsnNode) in1a;
                         if (in1b.desc.startsWith("Ljavax/swing/JTextField")) {
-//todo, check accessibleName
-                            AbstractInsnNode in2a = in1a.getNext();if(in2a==null)break;
+                            //todo, check accessibleName
+                            AbstractInsnNode in2a = in1a.getNext();
+                            if (in2a == null)
+                                break;
                             if (in2a.getOpcode() == Opcodes.INVOKEVIRTUAL) {
 
                                 MethodInsnNode in2b = (MethodInsnNode) in2a;

### 2016-04-01 src/main/java/guicat/config/GCConfig.java

@@ -64,7 +64,10 @@ public class GCConfig {
     }
 
     public static void main(String[] args) {
+        System.setProperty("guicat.conf", "./conf/barad-ticket/guicat.properties");
+        String a = System.getProperty("guicat.conf");
         GCConfig gcc =  GCConfig.getInstance();
+        System.out.println(gcc.config.toString());
         GCEntry gce = gcc.config.get("Name");
         System.out.println(gce.methodName);
     }

### 2016-04-01 src/main/java/guicat/config/GCEntry.java

@@ -1,9 +1,11 @@
 package guicat.config;
 
+import java.io.Serializable;
+
 /**
  * Created by oliver on 24/02/16.
  */
-public class GCEntry {
+public class GCEntry  {
     public String accessibleName;
     public String methodName;
     public String symbolicType;
@@ -14,5 +16,10 @@ public class GCEntry {
         this.methodName = mName;
         this.symbolicType = sType;
         this.initString = initString;
+
+    }
+
+    public String toString() {
+        return ">"+accessibleName+":"+methodName+":"+symbolicType+":"+initString+"<";
     }
 }

### 2016-04-01 doc/paper/james/2016_ASE_ChengLin/make.sh
rm doc

@@ -1,3 +1,0 @@
-#! /bin/bash
-paper=paper
-pdflatex $paper && bibtex $paper && pdflatex $paper && evince "paper.pdf"

### 2016-04-01 guicat-catg.sh

@@ -1,0 +1,59 @@
+#!/usr/bin/env bash
+if [ -z $1 ]; then
+    echo "Usage: ./guicat ./conf/ticket/ticket.conf"
+    exit
+fi
+
+#. ./conf/ticket/ticket.conf
+. $1
+
+classpath="."
+for jar in `ls lib`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./lib/"$jar
+    fi
+done
+
+for jar in `ls aut`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./aut/"$jar
+    fi
+done
+
+for jar in `ls $libDir`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":"$libDir"/"$jar
+    fi
+done
+
+echo $libDir
+echo $classpath
+
+
+
+mkdir branches/
+./clean.sh
+
+
+for testcase in `find $AUTTESTCASE -type f -name "*.tst" -printf '%f\n'`
+do
+    testcase_id=${testcase%????}
+    python concolic.py -Dguicat.conf=$guicatConfigFile -v 32 --autosym -t $testcase_id edu.umd.cs.guitar.replayer.JFCReplayerMain "-c $AUT_MAINCLASS -g $guiFile -e $efgFile -t $AUTDIR/testcases/$testcase_id.tst -i 2000 -d 200 -l $AUTDIR/logs/$testcase_id.log -gs $AUTDIR/states/$testcase_id.sta -cf $configurationFile -ts"
+#break
+done
+
+mv branches $AUTDIR
+
+#create guicat testcases
+cmd="java -Dguicat.conf=$guicatConfigFile -cp $classpath guicat.testcase.Generator $guiFile $AUTTESTCASE $branchDir $autGuicatTestcase"
+echo $cmd
+eval $cmd
+
+./jacoco.sh $AUT guitar
+./jacoco.sh $AUT guicat

### 2016-04-01 guicat-guitar.sh

@@ -1,0 +1,63 @@
+#!/usr/bin/env bash
+if [ -z $1 ]; then
+    echo "Usage: ./guicat ./conf/ticket/ticket.conf"
+    exit
+fi
+
+#. ./conf/ticket/ticket.conf
+. $1
+
+classpath="."
+for jar in `ls lib`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./lib/"$jar
+    fi
+done
+
+for jar in `ls aut`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":./aut/"$jar
+    fi
+done
+
+for jar in `ls $libDir`
+do
+    if [[ $jar == *.jar ]]
+    then
+        classpath=$classpath":"$libDir"/"$jar
+    fi
+done
+
+echo $libDir
+echo $classpath
+
+rm -rf $AUTDIR branches/
+mkdir $AUTDIR
+mkdir branches/
+mkdir $AUTDIR"/testcases"
+
+./clean.sh
+
+
+cmd="java -cp $classpath guicat.util.PrintAccessbileName $AUT_MAINCLASS"
+eval $cmd > $AUTDIR"/accessbileName.txt"
+
+
+ripperCmd="java -Dlog4j.configuration=$log4j -cp $classpath edu.umd.cs.guitar.ripper.JFCRipperMain -c $AUT_MAINCLASS -g $guiFile -cf $configurationFile -d 500 -i 2000 -l $logFile"
+eval $ripperCmd
+
+gui2efgCmd="java -Dlog4j.configuration=$log4j -cp $classpath  edu.umd.cs.guitar.graph.GUIStructure2GraphConverter -p EFGConverter -g $guiFile -e $efgFile"
+
+eval $gui2efgCmd
+
+testcaseCmd="java -Dlog4j.configuration=$logFile -cp $classpath  edu.umd.cs.guitar.testcase.TestCaseGenerator -p RandomSequenceLengthCoverage -e $efgFile -l 1 -m 200 -d $AUTTESTCASE"
+#testcaseCmd="java -Dlog4j.configuration=$log4j -cp $classpath  edu.umd.cs.guitar.testcase.TestCaseGenerator -p BytecodeAnalysis  -e $efgFile -l 2 -m 200 -d $AUTTESTCASE --scope ./aut/radioButton.jar  --method pair --shared 0"
+echo $testcaseCmd
+eval $testcaseCmd
+
+
+

### 2016-04-01 guicat-guitar.sh
fix mkdir bug

@@ -36,9 +36,9 @@ echo $libDir
 echo $classpath
 
 rm -rf $AUTDIR branches/
-mkdir $AUTDIR
-mkdir branches/
-mkdir $AUTDIR"/testcases"
+mkdir -p $AUTDIR
+mkdir -p branches/
+mkdir -p $AUTDIR"/testcases"
 
 ./clean.sh
 

### 2016-04-01 guicat.sh

@@ -36,9 +36,9 @@ echo $libDir
 echo $classpath
 
 rm -rf $AUTDIR branches/
-mkdir $AUTDIR
-mkdir branches/
-mkdir $AUTDIR"/testcases"
+mkdir  -p $AUTDIR
+mkdir -p branches/
+mkdir -p $AUTDIR"/testcases"
 
 ./clean.sh
 
